Molecular Gas Kinematics and Star Formation Properties of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231

### 2017-01-10 WRITEUP/ms.tex
resubmit

\input{preamble}
\slugcomment{To be submitted to the ApJ, with changes from the referee report }
 \makeatletter
% \renewcommand\normalsize{\@setfontsize\normalsize\@xpt{11.56}}
\renewcommand\normalsize{\@setfontsize\normalsize{10.56}{11.4}}
\makeatother

@@

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
and (2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of $f_{\rm gas}$\eq18\pmm4\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find a lensing-corrected stellar mass of
$M_{*}$\eq(3\pmm1)\E{10}\,\Msun and a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU,
corresponding to a specific SFR and star formation efficiency that are comparable to non-quasar host 
disk galaxies at $z$\ssim1.
This together with a gas mass fraction following the redshift evolution indicates
that no evidence for quenching of star formation is seen in RXS\,J1131$-$1231.
This is in agreement with the elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
local value, suggesting that the bulk of the black hole 
mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\input{table_obsprop}

\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission towards the background source RXJ1131 in the PdBI data
at $\gtrsim$\,27$\sigma$ significance. Based on this measurement, we refine the redshift of RXJ1131 to
$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\footnote{This redshift is derived by fitting a double-Gaussian to
the de-lensed spectrum (\Fig{delensed})
instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our
redshift determination
due to differential lensing (see \Sec{differential}).
}. The emission is spatially and kinematically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is 20.3\,$\pm$\,0.6 Jy \kms. % see 15May16/

@@

\begin{figure}[!htbp]
%\centering
\includegraphics[trim=12 27 0 1, clip, width=0.475\textwidth]{../Figures/F555W_ContPdBI.eps}
\includegraphics[trim=10 5 0 0, clip, width=0.4695\textwidth]{../Figures/F555W_ContVLA.eps}
\caption{Top: overlay of the PdBI 2\,mm continuum emission on the optical image.
Contours start and increment in steps of
$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne.
Bottom: overlay of the VLA 5\,GHz continuum emission on the optical image.
Contours correspond to $\pm2^n\sigma$, where
$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne
and $n$ is an integer running from 2 to 5.
Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$ significance.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$ for
the PdBI observations (top), and
0\farcs5 $\times$ 0\farcs4 (PA = 0.18$\degr$) for
the VLA observations (bottom).
\label{fig:cont}}\vspace{0.51em}
\end{figure}

@@

\subsection{Lens Modeling} \label{sec:lensmodel}
At the angular resolution of the \bco data, the source is resolved
$\gtrsim$2 resolution elements.
Given the extent of the lensed emission (see \Fig{CO21mom}),
this implies that we do not resolve
structures (e.g. knots and arcs) of the lensed emission
in our \bco data.
Nevertheless, the high spectral
resolution of these data provides kinematic information on
spatial scales smaller than the beam (see \Fig{CO21mom}).
Hence, we reconstruct the intrinsic line profile and source-plane velocity structure
% - morphology of different kinematic components - velocity structure
by carrying out a parametric lens modeling over different
channel slices of the interferometric data using our lensing code
\uvmcmcfit
(\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of the code).
Our approach follows a similar strategy as \citet{Riechers08a}, who reconstruct a source-plane
velocity gradient and constrain the gas dynamics in the $z$\,$>$\,4 quasar host galaxy of
 PSS J2322$+$1944,
which is also lensed into an Einstein ring configuration.
To ensure adequate SNRs for lens modeling, we bin the frequency channels by a factor of five
to produce seven independent $\Delta v$\,$\sim$\,105\,\kms channels (dashed line in \Fig{delensed})
that cover the full linewidth of $\sim$750\,\kms.

@@

Our code uses an Markov Chain Monte Carlo (MCMC) approach to sample the
posterior probability distribution function (PDF) of the model parameters.
In each model, we require a target acceptance rate of $\sim$0.25$-$0.5
and check for chain convergence by inspecting trace plots
and by requiring that the samples are obtained beyond at least an autocorrelation time.
We thus employ $\sim$50,000 samples as the initial ``burn-in'' phase
to stabilize the Markov chains (which we then discard) and
use the final $\sim$5,000 steps, sampled by 128 walkers, to identify
the posterior. Here, we
identify the best-fit model and the quoted uncertainties using the
median and the 68\% confidence intervals in the marginal PDFs.
\input{table_medianLens}

@@

Previous studies of RXJ1131 find evidence for differential lensing across
the {\it HST} $V$-, $I$-, and $H$-bands, where the
magnification factor varies from 10.9 to 7.8 \citepalias{Claeskens06a}.
This indicates that emission from different stellar populations
within the host galaxy are dissimilar with respect to the caustic.
%This imply that different stellar populations in the host galaxy are not co-spatial, and have
%different spatial extents, or
%may be a result of dust extinction and reddening.
The best-fit lens models obtained here for different CO channel slices show that differential lensing also plays
an important role in the observed \bco emission, with a magnification factor $(\mu_{\rm L})$ that varies
from 8.7 to 3.1 across different kinematic components (\Tab{model}).
The asymmetry in the line profile (\Fig{co21spec} and \Fig{delensed}) is therefore predominantly a result of
the redshifted CO-emitting gas being more strongly-magnified
than the
blueshifted component.
A secondary reason is likely due to 
the inclusion of the emission of the companion in the most redshifted velocity channels.
The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
positions relative to the caustics in \Fig{model}, where the red wing
emission mainly originates near the cusp
of the caustic and the blue wing emission is located beyond the caustics.
In fact, the intrinsic line flux of the redshifted and
blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
are $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively,
implying an intrinsically symmetric line profile (\Fig{delensed}). This is consistent with the symmetric source-plane
velocity gradient in our lens model (\Fig{model} and \Fig{PV}).
% The difference in magnification factors between CO and optical-to-NIR
% may further indicate that the CO emitting region is more extended and/or
% has a spatial offset from the optical-to-NIR emission
% (\ie different positions and alignment relative to the caustics) given
% the lower magnification factor found for CO (median $\mu_{\rm L}$ = 5.5)
% than in NIR, while their spatial extents appear to be similar. But then it could just be because of the low resolution and
% the degeneracy between the intrinsic source size and the magnification factor.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% gas to dust ratio:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Solomon+97: GDR ~ 100
% single disk: 90 (converted conversion factor to 0.8) (Sanders91a)
% our galaxy MW ~150 (Draine+07)
% 120 (Li & Draine 2001) to ?160 (Zubko et al. 2004) to ?180 (Draine et al. 2007, and references therein)
% Wilson+08: U/LIRGs: abstract: 120+/-28 (rms deviation 109) in the most central kpc; paper content: 215+/-53 (rms 207); but 50-70 for ULIRGs only
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Using the lensing-corrected dust mass, we find a galactic-scale %galaxy-wide
gas-to-dust ratio (GDR) of
54\pmm13.   %  (1.38e2+0.192e2)/16*5.5 +/- ((0.33/1.38)**2+(0.09/1.92)**2 + (12/16)**2)**.5*54
This GDR is lower than the statistical average of 206
in the \citetalias{Combes13a} sample but is well within the broad
range of values measured over their entire sample ($\sim$1$-$770).
Our ratio is also consistent with high-$z$ SMGs
% \citep[78\pmm26;][]{Bothwell13a}
\citep[]{Bothwell13a} and
local ULIRGs \citep{Wilson08a}, but lower than that of the Milky Way by
$\sim 7\sigma$ \citep[ignoring systematic uncertainties;][]{Li01a,Zubko04a,Draine07a}.

@@

% in terms of LFIR/L'CO:
% Greve+05: SMG 360 +/- 140 Lsun (K km/s pc^2)^-1
% Solomon97a: LFIR/L'CO = 160
% Daddi+10:  We find that the average SFE (in units of L? K?1 km?1 s pc?2) of BzK galaxies is 84\pmm12, that of SMGs is 390\pmm60, for QSOs we find 590\pmm100, for local ULIRGs we have 250\pmm30, and local spirals have 48\pmm7. Therefore, the typical BzK galaxy has about 80\% higher SFE of that of a local spiral, but individual values are well within the range measured for local spirals even though BzKs are a hundred times more luminous. Local ULIRGs have SFEs that are three times larger on average than BzK galaxies.
To first order, the star formation efficiency
$($SFE = \LFIR$/$$M_{\rm gas})$ indicates the \SF rate per unit solar mass of molecular gas available in a galaxy.
Using a wavelength range of 40\,$-$\,500\,$\micron$ defined
in \citetalias{Combes13a} for the far-IR luminosity,
we find an SFE of 58\pmm10 \Lsun $M_{\odot}^{-1}$, % I believe here we are taking the gas mass of both into account since we we couldn't separate out the LIR
which is on the low end among other U/LIRGs at $z$\,$<$\,0.6
% \citep[$\sim$180\pmm160 \Lsun $M_{\odot}^{-1}$;][]{Solomon97a, Combes11a}
\citep[\citetalias{Solomon97a};][]{Combes11a} but consistent with those of
low-$z$ spiral galaxies \citepalias[$z$\,$<$\,0.1;][]{SV05a} and high-$z$ disk-like
galaxies, which are also IR luminous galaxies with \LIR$\sim$10$^{12}$\,\Msun \citep{Daddi08a, Daddi10a}.
This suggests that the merger system is converting gas into stars at an efficiency
similar to those of ``normal'' star-forming
disk-like galaxies rather than starburst galaxies
\citep[][\citetalias{Combes13a}]{Tacconi08a, Riechers11a}.
This is in agreement with its disk-like kinematic signatures and its extended molecular gas distribution.
% Depletion time:
% Greve+05: ~40 Myr
Assuming the \SF continues at the current rate without gas replenishment,
the SFE corresponds to a
gas depletion time of $\tau$\,=\,102\pmm25\,Myr.

%
% %Tacconi13a: the best-fit MS, SFR would be 12.1 Msun/yr for MS given Mstar = 3e10.
% %sSFR (Gyr^-1) = 0.68 (Mstar/6.6e10)^-0.35((1+z)/2.2)^2.8 = 0.40 if RXJ on MS
The specific star formation rate (sSFR\eq SFR/$M_*$) of 4\petm{2.6}{2.4}\,Gyr\pmOne derived for RXJ1131
is $\lesssim$1.5$\sigma$ above the main sequence according to
the redshift-dependent ``main sequence'' relation in \citet[and references therein]{Tacconi13a}.
%  and is consistent with those of the \cite{dacunha10a} sample of local ULIRGs.
Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
the small elevation in sSFR over the main sequence at $z$\ssim0.7 suggests
that the \SF activity in RXJ1131 may be enhanced by interactions with the companion.
In addition, a SFE and sSFR comparable to those of high-$z$ disk 
galaxies, which are not known to host AGNs,
together with a molecular gas mass fraction that follows the redshift evolution reported in other studies (\Sec{frac})
suggest that no quenching of star formation is observed in RXJ1131, despite 
that fact that it is hosting a quasar.
Hence, the decline in star formation history since $z$\ssim2 
for at least a subset of AGN host galaxies 
may be mainly
a manifestation of the evolution in the molecular gas content rather than a result of 
the negative feedback driven by their central AGNs.

@@

\citet[]{Sluse07a} report two sets of AGN lines observed in RXJ1131.
The first set of lines is at $z$\ssim0.654, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at
$z_{\rm s, QSO}$\ssim0.658, including the broad component of the Balmer lines and the \mgii emission line.
Using the CO line center redshift as the systemic redshift,
we find that the redshift of the first set is fully consistent with the systemic redshift. This
supports previous claims that [O\,{\scriptsize III}] lines, tracing the narrow line region (NLR),
are good proxies
to the true systemic redshift \citep[e.g.,][]{Vrtilek85a, Nelson00a}.
On the other hand, the second set of lines is redshifted by $\sim$715\,\kms.
Velocity offsets between broad line region (BLR) and NLR lines have been reported in literature.
\citet{Richards02a} find a median offset of
% median of 97\kms and a dispersion of 269\,\kms in the distribution of offset
$\sim$100\pmm270\,\kms
between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines in a
sample of $>$3800 quasars,
and \citet{Bonning07a} report
a mean offset of
% a mean offset of
% 100\,\kms with a dispersion of 212\,\kms
%FWHM = 500
$\sim$100\pmm210\,\kms
between the broad component of
H$\beta$ and [O\,{\scriptsize III}] lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.8,
where only $\lesssim$20 of them (i.e., $<$1\%) are found to have offsets $>$800\,\kms
and $\sim$1\% 
are found to have offsets $>$500\,\kms \footnote{\citet{Bonning07a} report the fraction of objects with offset velocities greater 
than 500, 800, 1000, 1500, 2000, and 2500\,\kms. We therefore quote the two fractions corresponding to 
offset velocities closest 
to that of RXJ1131 ($\sim$715\,\kms) in this discussion.}
Thus, large velocity offsets between BLR and NLR lines
comparable to that of RXJ1131 are uncommon but have been observed in some cases.

@@

Theoretical studies have suggested that negative feedback from an AGN may remove a 
large fraction of the molecular gas from its host galaxy, thereby quenching its star formation \mbox{\citep[e.g., ][]{DiMatteo05a}}.
In this study, we find that the star formation efficiency and specific SFR derived for RXJ1131 are comparable to those of 
non-AGN host disk galaxies at $z$\ssim1$-$1.5, and that the 
derived molecular gas mass fraction is consistent with the redshift evolution reported in other studies. 
We thus find no evidence of negative AGN feedback on the molecular gas content 
and on the star formation activity in RXJ1131 at the resolution of our data.
Our results may be hinting that at least for a subset of AGN host galaxies at intermediate redshift,
their contribution to the decline in cosmic star formation history since $z$\ssim2 
may be mainly
a manifestation of the redshift evolution in the molecular gas content rather than a result of 
negative feedback driven by their central AGNs.

Using the CO redshift as systemic redshift for the host galaxy of RXJ1131, we find
that the redshift inferred from NLR lines reported in previous studies are consistent with this systemic redshift
but that the BLR lines are redshifted by $\sim$715\,\kms.
We raise several plausible scenarios that may explain the observed velocity offset, \eg
outflow/inflow of gas in the BLR, kinematics of the accretion disk, geometric effects,
microlensing, and a recoiling black hole from merger event.
The latter scenario might also explain the high black hole spin parameter of 
$a$\eq0.87\petm{0.08}{0.15} reported by \citet[][]{Reis14a}, but
further evidence is needed to confirm or rule out this scenario.
% spin up scenario:
% Wang+16: """ The spin of a BH is widely believed to play a crucial role in
% determining the radio emission from SMBHs. The scenario that
% an energy is extracted from an SMBH being spun up by a BH?
% BH merger (e.g., Chiaberge & Marconi 2011) is favored for
% high-mass SMBHs. This spin-up scenario is, however, almost
% infeasible for low-mass SMBHs because they are believed to
% largely build from secular evolution driven by internal
% dynamical processes in the disk growth rather than from two
% BHs merging (e.g., Kormendy & Ho 2013).

>>>>

\input{preamble}
\slugcomment{With changes from the referee report}
 \makeatletter
% \renewcommand\normalsize{\@setfontsize\normalsize\@xpt{11.56}}
\renewcommand\normalsize{\@setfontsize\normalsize{10.56}{11.4}}
\makeatother

@@

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile and a smooth source-plane velocity
gradient suggest that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
We also find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
and (2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
We find a lensing-corrected stellar mass of
$M_{*}$\eq(3\pmm1)\E{10}\,\Msun and a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU,
corresponding to a specific SFR and star formation efficiency comparable to  
$z$\ssim1 disk galaxies not hosting quasars.
The implied gas mass fraction of $\sim$18\pmm4\% is consistent with the previously-observed cosmic decline since $z$\ssim2. We thus find no evidence for quenching of star formation in RXS\,J1131$-$1231. This agrees with our finding of an elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
local value, suggesting that the bulk of its black hole 
mass is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission towards the background source RXJ1131 in the PdBI data
at $\gtrsim$\,27$\sigma$ significance. Based on this measurement, we refine the redshift of RXJ1131 to
$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\footnote{This redshift is derived by fitting a double-Gaussian to
the de-lensed spectrum (\Fig{delensed})
instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our
redshift determination
due to differential lensing (see \Sec{differential}).
}. The emission is spatially and kinematically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is 20.3\,$\pm$\,0.6 Jy \kms. % see 15May16/

\input{table_obsprop}

@@

\begin{figure}[!htbp]
\includegraphics[trim=12 27 0 1, clip, width=0.47\textwidth]{../Figures/F555W_ContPdBI.eps}
\includegraphics[trim=10 5 0 0, clip, width=0.47\textwidth]{../Figures/F555W_ContVLA.eps}
\caption{Top: overlay of the PdBI 2\,mm continuum emission on the optical image.
Contours start and increment in steps of
$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne.
Bottom: overlay of the VLA 5\,GHz continuum emission on the optical image.
Contours correspond to $\pm2^n\sigma$, where
$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne
and $n$ is an integer running from 2 to 5.
Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$ significance.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$ for
the PdBI observations (top), and
0\farcs5 $\times$ 0\farcs4 (PA = 0.18$\degr$) for
the VLA observations (bottom).
\label{fig:cont}}\vspace{0.51em}
\end{figure}

@@

\subsection{Lens Modeling} \label{sec:lensmodel}
At the angular resolution of the \bco data, the source is resolved
$\gtrsim$2 resolution elements.
Given the extent of the lensed emission (see \Fig{CO21mom}),
this implies that we do not resolve
structures (e.g. knots and arcs) of the lensed emission
in our \bco data.
Nevertheless, the high spectral
resolution of these data provides kinematic information on
spatial scales smaller than the beam (see \Fig{CO21mom}).
Hence, we reconstruct the intrinsic line profile and source-plane velocity structure
% - morphology of different kinematic components - velocity structure
by carrying out a parametric lens modeling over different
channel slices of the interferometric data using our lensing code
\uvmcmcfit
(\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of the code).
Our approach follows a similar strategy as \citet{Riechers08a}, who reconstruct a source-plane
velocity gradient and constrain the gas dynamics in the $z$\,$>$\,4 quasar host galaxy of
 PSS J2322$+$1944,
which is also lensed into an Einstein ring configuration.
To ensure adequate SNRs for lens modeling, we bin the frequency channels by a factor of five
to produce seven independent $\Delta v$\,$\sim$\,105\,\kms channels (dashed line in \Fig{delensed})
that cover the full linewidth of $\sim$750\,\kms.
\input{table_medianLens}

@@

Our code uses an Markov Chain Monte Carlo (MCMC) approach to sample the
posterior probability distribution function (PDF) of the model parameters.
In each model, we require a target acceptance rate of $\sim$0.25$-$0.5
and check for chain convergence by inspecting trace plots
and by requiring that the samples are obtained beyond at least an autocorrelation time.
We thus employ $\sim$50,000 samples as the initial ``burn-in'' phase
to stabilize the Markov chains (which we then discard) and
use the final $\sim$5,000 steps, sampled by 128 walkers, to identify
the posterior. Here, we
identify the best-fit model and the quoted uncertainties using the
median and the 68\% confidence intervals in the marginal PDFs.

@@

Previous studies of RXJ1131 find evidence for differential lensing across
the {\it HST} $V$-, $I$-, and $H$-bands, where the
magnification factor varies from 10.9 to 7.8 \citepalias{Claeskens06a}.
This indicates that the emission from different stellar populations
within the host galaxy have various spatial extents and positions with respect to the caustic.
%may be a result of dust extinction and reddening.
The best-fit lens models obtained here for different CO channels show that differential lensing also plays
an important role in the observed \bco emission, with a magnification factor $(\mu_{\rm L})$ that varies
from 8.7 to 3.1 across different kinematic components (\Tab{model}).
The asymmetry in the line profile (\Fig{CO21spec} and \Fig{delensed}) is therefore predominantly a result of
the redshifted CO-emitting gas being more strongly-magnified
than the
blueshifted component.
A secondary reason is likely due to 
the inclusion of the emission of the companion in the most redshifted velocity channels.
The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
positions relative to the caustics in \Fig{model}, where the red wing
emission mainly originates near the cusp
of the caustic and the blue wing emission is located beyond the caustics.
In fact, the intrinsic line flux of the redshifted and
blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
are $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively,
implying an intrinsically symmetric line profile (\Fig{delensed}). This is consistent with the symmetric source-plane
velocity gradient in our lens model (\Fig{model} and \Fig{PV}).
% The difference in magnification factors between CO and optical-to-NIR
% may further indicate that the CO emitting region is more extended and/or
% has a spatial offset from the optical-to-NIR emission
% (\ie different positions and alignment relative to the caustics) given
% the lower magnification factor found for CO (median $\mu_{\rm L}$ = 5.5)
% than in NIR, while their spatial extents appear to be similar. But then it could just be because of the low resolution and
% the degeneracy between the intrinsic source size and the magnification factor.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% gas to dust ratio:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Solomon+97: GDR ~ 100
% single disk: 90 (converted conversion factor to 0.8) (Sanders91a)
% our galaxy MW ~150 (Draine+07)
% 120 (Li & Draine 2001) to ?160 (Zubko et al. 2004) to ?180 (Draine et al. 2007, and references therein)
% Wilson+08: U/LIRGs: abstract: 120+/-28 (rms deviation 109) in the most central kpc; paper content: 215+/-53 (rms 207); but 50-70 for ULIRGs only
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Using the lensing-corrected dust mass, we find a galactic-scale %galaxy-wide
gas-to-dust ratio (GDR) of
54\pmm13.   %  (1.38e2+0.192e2)/16*5.5 +/- ((0.33/1.38)**2+(0.09/1.92)**2 + (12/16)**2)**.5*54
This would be higher by a factor of two if we were to adopt a dust mass from the other SED fit that is unconstrained at 24\,$\micron$.
This GDR is lower than the statistical average of 206
in the \citetalias{Combes13a} sample but is well within the broad
range of values measured over their entire sample ($\sim$1$-$770).
Our ratio is also consistent with high-$z$ SMGs
% \citep[78\pmm26;][]{Bothwell13a}
\citep[]{Bothwell13a} and
local ULIRGs \citep{Wilson08a}, but lower than that of the Milky Way by
$\sim 7\sigma$ \citep[ignoring systematic uncertainties;][]{Li01a,Zubko04a,Draine07a}.

@@

% in terms of LFIR/L'CO:
% Greve+05: SMG 360 +/- 140 Lsun (K km/s pc^2)^-1
% Solomon97a: LFIR/L'CO = 160
% Daddi+10:  We find that the average SFE (in units of L? K?1 km?1 s pc?2) of BzK galaxies is 84\pmm12, that of SMGs is 390\pmm60, for QSOs we find 590\pmm100, for local ULIRGs we have 250\pmm30, and local spirals have 48\pmm7. Therefore, the typical BzK galaxy has about 80\% higher SFE of that of a local spiral, but individual values are well within the range measured for local spirals even though BzKs are a hundred times more luminous. Local ULIRGs have SFEs that are three times larger on average than BzK galaxies.
To first order, the star formation efficiency
$($SFE = \LFIR$/$$M_{\rm gas})$ indicates the \SF rate per unit solar mass of molecular gas available in a galaxy.
Using a wavelength range of 40\,$-$\,500\,$\micron$ defined
in \citetalias{Combes13a} for the far-IR luminosity,
we find an SFE of 58\pmm10 \Lsun $M_{\odot}^{-1}$, % I believe here we are taking the gas mass of both into account since we we couldn't separate out the LIR
which is on the low end among other U/LIRGs at $z$\,$<$\,0.6
% \citep[$\sim$180\pmm160 \Lsun $M_{\odot}^{-1}$;][]{Solomon97a, Combes11a}
\citep[\citetalias{Solomon97a};][]{Combes11a} but consistent with those of
low-$z$ spiral galaxies \citep[$z$\,$<$\,0.1;][]{SV05a} and high-$z$ disk-like
galaxies, which are also IR luminous galaxies with \LIR$\sim$10$^{12}$\,\Msun \citep{Daddi08a, Daddi10a}.
This suggests that the merger system is converting gas into stars at an efficiency
similar to those of ``normal'' star-forming
disk-like galaxies rather than starburst galaxies
\citep[][\citetalias{Combes13a}]{Tacconi08a, Riechers11a}.
This is in agreement with its disk-like kinematic signatures and its extended molecular gas distribution.
% Depletion time:
% Greve+05: ~40 Myr
Assuming the \SF continues at the current rate without gas replenishment,
the SFE corresponds to a
gas depletion time of $\tau$\,=\,102\pmm25\,Myr.

%
% %Tacconi13a: the best-fit MS, SFR would be 12.1 Msun/yr for MS given Mstar = 3e10.
% %sSFR (Gyr^-1) = 0.68 (Mstar/6.6e10)^-0.35((1+z)/2.2)^2.8 = 0.40 if RXJ on MS
The specific star formation rate (sSFR\eq SFR/$M_*$) of 4\petm{2.6}{2.4}\,Gyr\pmOne derived for RXJ1131
is $\lesssim$1.5$\sigma$ above the main sequence according to
the redshift-dependent ``main sequence'' relation in \citet[and references therein]{Tacconi13a}.
%  and is consistent with those of the \cite{dacunha10a} sample of local ULIRGs.
Given that RXJ1131 shares similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
the small elevation in sSFR over the main sequence at $z$\ssim0.7 suggests
that the \SF activity in RXJ1131 may be enhanced by interactions with the companion.

@@

\citet[]{Sluse07a} report two sets of AGN lines observed in RXJ1131.
The first set of lines is at $z$\ssim0.654, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at
$z_{\rm s, QSO}$\ssim0.658, including the broad component of the Balmer lines and the \mgii emission line.
Using the CO line center redshift as the systemic redshift,
we find that the redshift of the first set is fully consistent with the systemic redshift. This
supports previous claims that [O{\scriptsize III}] lines, tracing the narrow line region (NLR),
are good proxies
to the true systemic redshift \citep[e.g.,][]{Vrtilek85a, Nelson00a}.
On the other hand, the second set of lines is redshifted by $\sim$715\,\kms.

Velocity offsets between broad line region (BLR) and NLR lines have been reported in literature.
\citet{Richards02a} find a median offset of
% median of 97\kms and a dispersion of 269\,\kms in the distribution of offset
$\sim$100\pmm270\,\kms
between [Mg{\scriptsize II}] and [O{\scriptsize III}] lines in a
sample of $>$3800 quasars,
and \citet{Bonning07a} report
a mean offset of
% a mean offset of
% 100\,\kms with a dispersion of 212\,\kms
%FWHM = 500
$\sim$100\pmm210\,\kms
between the broad component of
H$\beta$ and [O{\scriptsize III}] lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.8,
where only $\lesssim$20 of them (i.e., $<$1\%) are found to have offsets $>$800\,\kms
and $\sim$1\% 
are found to have offsets $>$500\,\kms \footnote{\citet{Bonning07a} report the fraction of objects with offset velocities greater 
than 500, 800, 1000, 1500, 2000, and 2500\,\kms. We therefore quote the two fractions corresponding to 
offset velocities closest 
to that of RXJ1131 ($\sim$715\,\kms) in this discussion.}
Thus, large velocity offsets between BLR and NLR lines
comparable to that of RXJ1131 are uncommon but have been observed in some cases.

@@

We find that the redshift inferred from the NLR lines reported in previous studies are consistent with the  systemic redshift as measured
from the CO line,
but that the BLR lines are redshifted by $\sim$715\,\kms.
We raise several plausible scenarios that may explain the observed velocity offset, \eg
outflow/inflow of gas in the BLR, kinematics of the accretion disk, geometric effects,
microlensing, and a recoiling black hole from merger event.
The latter scenario might also explain the high black hole spin parameter of 
$a$\eq0.87\petm{0.08}{0.15} reported by \citet[][]{Reis14a}, but
further evidence is needed to confirm or rule out this scenario.
% spin up scenario:
% Wang+16: """ The spin of a BH is widely believed to play a crucial role in
% determining the radio emission from SMBHs. The scenario that
% an energy is extracted from an SMBH being spun up by a BH?
% BH merger (e.g., Chiaberge & Marconi 2011) is favored for
% high-mass SMBHs. This spin-up scenario is, however, almost
% infeasible for low-mass SMBHs because they are believed to
% largely build from secular evolution driven by internal
% dynamical processes in the disk growth rather than from two
% BHs merging (e.g., Kormendy & Ho 2013).
